---
title: "beta_vis"
author: "Nick Gondek"
date: "April 4, 2016"
output: html_document
---

This rmd will take in the file created by g0b_summary.R (and perhaps the equivalent versions for the models without a behavior parameter, yet to exist) and look at the g0's versus size and sub

```{r message=FALSE}
library(ggplot2) ## <3 ggplot
library(dplyr) ## Also <3 dplyr
library(reshape2)
library(cowplot)
```

Read in aforementioned csv file - rownames null because they're all 1, we'll drop that column
```{r, echo=TRUE}
g0est<-read.csv("../data/SubsamplingData/g0bTRUE_est.csv", row.names = NULL)
g0est<-g0est[2:4]
```

get the g0 from the full models in order to compare with subsamples. g0.bTRUE by g0 on the variance covariance matrix.
```{r}
fullg0b_A<-readRDS("VerificationObjects/ModelAFull.rds")$beta.vcv["g0.bTRUE", "g0"] 
fullg0b_C<-readRDS("VerificationObjects/ModelCFull.rds")$beta.vcv["g0.bTRUE", "g0"]
fullg0b_E<-readRDS("VerificationObjects/ModelEFull.rds")$beta.vcv["g0.bTRUE", "g0"]

fullg0_A<-readRDS("VerificationObjects/ModelAFull.rds")$beta.vcv["g0", "g0"] 
fullg0_B<-readRDS("VerificationObjects/ModelCFull.rds")$beta.vcv["g0", "g0"]
fullg0_C<-readRDS("VerificationObjects/ModelEFull.rds")$beta.vcv["g0", "g0"]
```


ggplot boxplot of subtype versus g0bTRUE.
```{r}
ggplot(g0est[g0est$Model == "Model A",], aes(x=Subtype, y=g0.bTRUE, col=Subtype)) + 
  geom_boxplot(notch=TRUE) +
  ggtitle("Model A : g0~b+t+Sex") +
  geom_hline(aes(yintercept=fullg0b_A)) +
  scale_color_brewer(palette="Dark2") +
  theme(legend.position="none")

ggplot(g0est[g0est$Model == "Model C",], aes(x=Subtype, y=g0.bTRUE, col=Subtype)) + 
  geom_boxplot(notch=TRUE) +
  ggtitle("Model C : g0~b+t") +
  geom_hline(aes(yintercept=fullg0b_C)) +
  scale_color_brewer(palette="Dark2") +
  theme(legend.position="none")

ggplot(g0est[g0est$Model == "Model E",], aes(x=Subtype, y=g0.bTRUE, col=Subtype)) + 
  geom_boxplot(notch=TRUE) +
  ggtitle("Model E : g0~b") +
  geom_hline(aes(yintercept=fullg0b_E)) +
  scale_color_brewer(palette="Dark2") +
  theme(legend.position="none")
```

Now looking at size.
```{r}
g0est<-read.csv("../data/SizeData/g0bTRUE_est.csv", row.names = NULL)
g0est<-g0est[2:6]
colnames(g0est)<-c("g0","g0.bTRUE", "Model", "Subtype", "Size")
```

g0 and g0bTRUE on one facet graph 
```{r}
g0melt<-melt(g0est, na.rm = FALSE, id.vars = c("Model","Subtype", "Size"))
dummyA<-data.frame(var = c("g0", "g0b_TRUE"), full=c(fullg0b_A, fullg0_A))


a<-ggplot(filter(g0melt, Model=="Model A", variable=="g0"), aes(x=as.factor(Size), y=value)) + 
  geom_boxplot(notch=FALSE) +
  ggtitle("g0~b+t+Sex") +
  facet_grid(.~Subtype)+
  xlab("") +
  ylab("g0")+
  theme(strip.text.x = element_text(size=16),axis.text.x = element_text(angle = 90, hjust = 1))+
  scale_color_brewer(palette="Dark2") +
  theme(legend.position="none") +
  geom_hline(aes(yintercept=fullg0_A), col="red") +
  theme_gray()


b<-ggplot(filter(g0melt, Model=="Model A", variable=="g0.bTRUE"), aes(x=as.factor(Size), y=value)) + 
  geom_boxplot(notch=FALSE) +
  ggtitle("g0~b+t+Sex") +
  facet_grid(.~Subtype)+
  xlab("") +
  ylab("g0b")+
  theme(strip.text.x = element_text(size=16),axis.text.x = element_text(angle = 90, hjust = 1))+
  scale_color_brewer(palette="Dark2") +
  theme(legend.position="none") +
  geom_hline(aes(yintercept=fullg0b_A), col="red") +
  theme_gray()

plot_grid(a,b,ncol = 1, nrow=2)
```

ggplots of size data.
```{r}
ggplot(filter(g0est, Model=="Model C", Subtype == "Spread.one"), aes(x=as.factor(Size), y=g0.bTRUE)) + 
  geom_boxplot(notch=FALSE) +
  ggtitle("Model C : g0~b+t, Spread.one") +
  geom_hline(aes(yintercept=fullg0b_C)) +
  scale_color_brewer(palette="Dark2") +
  theme(legend.position="none")

ggplot(filter(g0est, Model=="Model C", Subtype == "Spread.one"), aes(x=as.factor(Size), y=g0.bTRUE)) + 
  geom_boxplot(notch=FALSE) +
  ggtitle("Model C : g0~b+t, Spread.one") +
  geom_hline(aes(yintercept=fullg0b_C)) +
  scale_color_brewer(palette="Dark2") +
  theme(legend.position="none")

ggplot(filter(g0est, Model=="Model E", Subtype == "Spread.one"), aes(x=as.factor(Size), y=g0.bTRUE)) + 
  geom_boxplot(notch=FALSE) +
  ggtitle("Model E : g0~b, Spread.one") +
  geom_hline(aes(yintercept=fullg0b_E)) +
  scale_color_brewer(palette="Dark2") +
  theme(legend.position="none")

#Now for simplerandom
ggplot(filter(g0est, Model=="Model A", Subtype == "SimpleRandom"), aes(x=as.factor(Size), y=g0.bTRUE)) + 
  geom_boxplot(notch=FALSE) +
  ggtitle("Model A : g0~b+t+Sex, SimpleRandom") +
  geom_hline(aes(yintercept=fullg0b_A)) +
  scale_color_brewer(palette="Dark2") +
  theme(legend.position="none")

ggplot(filter(g0est, Model=="Model C", Subtype == "SimpleRandom"), aes(x=as.factor(Size), y=g0.bTRUE)) + 
  geom_boxplot(notch=FALSE) +
  ggtitle("Model C : g0~b+t, SimpleRandom") +
  geom_hline(aes(yintercept=fullg0b_C)) +
  scale_color_brewer(palette="Dark2") +
  theme(legend.position="none")

ggplot(filter(g0est, Model=="Model E", Subtype == "SimpleRandom"), aes(x=as.factor(Size), y=g0.bTRUE)) + 
  geom_boxplot(notch=FALSE) +
  ggtitle("Model E : g0~b, SimpleRandom") +
  geom_hline(aes(yintercept=fullg0b_E)) +
  scale_color_brewer(palette="Dark2") +
  theme(legend.position="none")
```

so what does the subsampling actually do to those 250 size subsamples that are wildly different? 
```{r}
g0b_sum_outliers <- function(subtype,treatment, mod, high=TRUE, size=250){
  if(high==TRUE){MAX<-0}else{MAX<-1}
  secrMAX<-NULL
    for(j in 4:30){ ##eyeball this upper bound... highest secr number goes here
       if(treatment=="Sub"){
        pathin<-paste("../data/SubsamplingData/", subtype,"/", mod,"/secr", j,"_", size,".rds", sep="")
      }
      
      if(treatment=="Size"){
        pathin<-paste("../data/SizeData/", subtype,"/", mod,"/secr", j,"_", size, ".rds", sep="")
      }
      
      try({ ##try() used because secr###.rds numbers have gaps, this is easiest/ugliest solution
        secrMod<-readRDS(pathin)
        bTru<-secrMod$beta.vcv["g0.bTRUE", "g0"] ##g0.bTRUE by g0 on the variance covariance matrix
        if (abs(bTru)>MAX & high==TRUE){secrMAX<-secrMod; MAX<-abs(bTru)}
        if (abs(bTru)<MAX & high==FALSE){secrMAX<-secrMod; MAX<-abs(bTru)}
          })
      
    }
        return(secrMAX)
}
```

Let's pull the highest and lowest 250 from either subsampling type.
```{r}
##high values
hi.spread<-vector(mode = "list", length = 3)
hi.spread[[1]]<-g0b_sum_outliers(subtype = "Spread.one", treatment = "Size", mod = "Model A", high = TRUE, size = 250)
hi.spread[[2]]<-g0b_sum_outliers(subtype = "Spread.one", treatment = "Size", mod = "Model C", high = TRUE, size = 250)
hi.spread[[3]]<-g0b_sum_outliers(subtype = "Spread.one", treatment = "Size", mod = "Model E", high = TRUE, size = 250)

hi.rand<-vector(mode = "list", length = 3)
hi.rand[[1]]<-g0b_sum_outliers(subtype = "SimpleRandom", treatment = "Size", mod = "Model A", high = TRUE, size = 250)
hi.rand[[2]]<-g0b_sum_outliers(subtype = "SimpleRandom", treatment = "Size", mod = "Model C", high = TRUE, size = 250)
hi.rand[[3]]<-g0b_sum_outliers(subtype = "SimpleRandom", treatment = "Size", mod = "Model E", high = TRUE, size = 250)

##low values
lo.spread<-vector(mode = "list", length = 3)
lo.spread[[1]]<-g0b_sum_outliers(subtype = "Spread.one", treatment = "Size", mod = "Model A", high = FALSE, size = 250)
lo.spread[[2]]<-g0b_sum_outliers(subtype = "Spread.one", treatment = "Size", mod = "Model C", high = FALSE, size = 250)
lo.spread[[3]]<-g0b_sum_outliers(subtype = "Spread.one", treatment = "Size", mod = "Model E", high = FALSE, size = 250)

lo.rand<-vector(mode = "list", length = 3)
lo.rand[[1]]<-g0b_sum_outliers(subtype = "SimpleRandom", treatment = "Size", mod = "Model A", high = FALSE, size = 250)
lo.rand[[2]]<-g0b_sum_outliers(subtype = "SimpleRandom", treatment = "Size", mod = "Model C", high = FALSE, size = 250)
lo.rand[[3]]<-g0b_sum_outliers(subtype = "SimpleRandom", treatment = "Size", mod = "Model E", high = FALSE, size = 250)
```

So now we have the models, but we need the subsamples, and I neglected to use a unique ID ket for each subsample and model, so... 
```{r eval=FALSE}
desnconv<-function(x){
   100*x/3861.022
}
desnconv(hi.rand[[1]])[2,c(1,3,4)]

```

