###This script is meant to rerun the models that John originally ran for SecrAll1 and SecrAll2. I noticed a discrepancy between the code and the document he prepared for Dave, and I'm not sure it makes a difference. But it's worth looking at. This will more or less be a copy of SecrAll1, with the 5 models I chose. 

# Initial SECR models 


```{r echo=FALSE}
# wd <- ifelse(basename(getwd())=="Rscripts", 
#               gsub("/Rscripts", "", getwd()),
#              getwd())
#  opts_knit$set(root.dir=wd,comment=NA, fig.height=8, fig.width=12)
#opts_knit$set(comment=NA, fig.height=8, fig.width=12, cache=TRUE)
rm(list = ls()) # clear out memory
```

Load libraries

```{r warning=FALSE, message=FALSE}
library(dplyr) # for data manipulation
library(secr) 
library(secrdesign)
library(scrbook)
library(ggplot2)
options(width=160)
```

## Initial data explorations
Lets look at the trapping grid.   


```{r }
trap.gr<-read.csv("../data/detectorfileScaled.csv", header=FALSE)
names(trap.gr)<-c("Trap", "X", "Y")
plot(trap.gr$X, trap.gr$Y, main="Trap Grid", xlab="X", ylab="Y") 
```

Read in data created using "Data Exploration.R" file, names(bearCH)<-c("Session", "ID", "Occasion", "Detector", "Count", "Sex")

```{r }
bearCH<-read.capthist("../data/BearCH.csv", "../data/detectorfileScaled.csv",  detector= 'proximity', covnames="Sex")
```

Try plotting method from scrbook package 

```{r }
enc<-read.csv("../data/BearCH.csv", header=F) # Encounter data
enc[,1]<-as.numeric(1) # Treat individuals and periods as factor variables
enc[,2]<-as.numeric(enc[,2])
traps<-read.csv("../data/detectorfileScaled.csv", header=FALSE) # Trap data
traps.3d<-cbind(traps, matrix(1, nrow(traps),6))  # add columns to say when traps were active
y3d<-SCR23darray(enc[,1:4], traps.3d) # Create 3d array from capture history
spiderplot(y3d, traps[,2:3]) # plot centroids along with recpatures for each individual
```

### Summary of the data provided by SECR

- n = number of individuals detected on each occasion
- u = number of individuals detected for the first time on each occasion
- f =  number of individuals detected exactly f times
- M(t+1) =  cumulative number of individuals detected
- losses	= number of individuals reported as not released on each occasion
- detections	= number of detections, including within-occasion `recaptures'
- detectors visited = number of detectors at which at least one detection was recorded
- detectors used =  number of detectors, excluding any `not set' in usage attribute of traps attribute

```{r }
summary(bearCH)
str(bearCH)
```

## Models 

First, explore the effect of scaling the trapping grid coordinates

- Model detection as a function of period, movement as function of sex
- Compare models fit using scaled and unscaled grid

Model detection as a function of capture Period and movement as a function of sex of the animal.
Buffer if scaled = 10, if unscaled = 10*10000 = 10,000

```{r }
secr0 <- secr.fit(bearCH, model =list(g0~t, sigma~Sex), buffer = 10, trace = FALSE, CL=TRUE) # null model
plot(secr0$mask)
plot(bearCH, tracks=T, add=T)
```

Calculate density estimate (a derived parameter)

```{r }
ds<-derived(secr0)
```

What if we use the unscaled and uncentered trap locations?

```{r }
bearCH.us<-read.capthist("../data/BearCH.csv", "../data/detectorfileUnScaled.csv",  detector= 'proximity', covnames="Sex")
summary(bearCH.us)
secr0.US <- secr.fit(bearCH.us, model =list(g0~t, sigma~Sex), buffer = 10000, trace = FALSE, CL=TRUE) # null model
dUS<-derived(secr0.US)
```

Compare density estimates (just different scales)  

```{r }
dUS # unscaled
ds  # scaled
```

Now, N in the region (these depend critically on the size of the buffer!).  Early on, I used a buffer size of 10 (for scaled) and a buffer
size of 50,000 for the unscaled. The latter buffer was much bigger (proporationally) and resulted in a much bigger N! Here, buffers are similar
and there is little to no difference between the estimates.

```{r }
region.N(secr0)
region.N(secr0.US)
```

Before moving forward, lets check the buffer = 10

```{r }
mask.check(secr0) #looks OK
```

## Models

In all of these models, I will assume sigma~sex (males move more than females)

-g0 ~  b + t + Sex

-g0 ~  t + Sex

-g0 ~  b + t

-g0 ~  t

-g0 ~  b


```{r }
secrA <- secr.fit(bearCH, model =list(g0~b+t+Sex, sigma~Sex), buffer = 10, trace = FALSE, CL=TRUE) # null model
(dA<-derived(secrA))
```

```{r }
secrB <- secr.fit(bearCH, model =list(g0~t+Sex, sigma~Sex), buffer = 10, trace = FALSE, CL=TRUE) # null model
(dB<-derived(secrB))
```

```{r }
secrC <- secr.fit(bearCH, model =list(g0~b+t, sigma~Sex), buffer = 10, trace = FALSE, CL=TRUE) # null model
(dC<-derived(secrC))
```

```{r }
secrD <- secr.fit(bearCH, model =list(g0~t, sigma~Sex), buffer = 10, trace = FALSE, CL=TRUE) # null model
(dD<-derived(secrD))
```

```{r }
secrE <- secr.fit(bearCH, model =list(g0~b, sigma~Sex), buffer = 10, trace = FALSE, CL=TRUE) # null model
(dE<-derived(secrE))
```

Compare models using AIC  

```{r }
AIC(secrA, secrB, secrC, secrD, secrE)
```

## Parameter estimates  

#### Model A

```{r }
secrA
```

#### Model B

```{r }
secrB
```

#### Model C  

```{r }
secrC
```

#### Model D

```{r }
secrD
```

#### Model E

```{r }
secrE
```

## Density estimates

Convert density esitmate to N/sq mile.  As reported on the help page for secr.fit:
  
  - Density for the unscaled analysis is reported in terms of animals/ha (with distances measured in m). So...
- For the scaled analysis, density will be reported in terms of animals/(1000x1000)ha (with distances measured 
                                                                                       in terms of km).  

There are 3861.022 square miles in 1000x1000 ha.  To convert, we use:
  
  D (per 100 $mi^2$) = (N/ha)*(1000ha/3.861022 mi^2)*100  


```{r }
desnconv<-function(x){
  100*x/3861.022
}
desnconv(dA[2,c(1,3,4)]) ## 95% confint
desnconv(dB[2,c(1,3,4)]) 
desnconv(dC[2,c(1,3,4)]) 
desnconv(dD[2,c(1,3,4)])  
desnconv(dE[2,c(1,3,4)]) 
```
